---
title       : Conversion between Metric Units and English Units
subtitle    : A Shiny Application
author      : P. Angzh
job         : Web Technology
framework   : io2012            # io2012, html5slides, shower, dzslides, ...
highlighter : highlight.js
hithem      : tomorrow
widgets     : []                # mathjax, quiz, bootstrap
mode        : selfcontained     # standalone, draft, selfcontained
knit        : slidify::knit2slides

--- .class #id

### Overview

This application does conversion between metric units and English units for the following measuememts:

  1. temperature (between Fahrenheit and Celsius)
  2. distance (between mile and kilometer)
  3. volume (between gallon and liter)

From the input page, you just select the type of conversion (e.g. F to C for converting temperatue from Fahrenheit to Celsius), enter a value, then click the Convert button to get the converted value.

--- .class #id

### Temperature Conversion between Fahrenheit (F) and Celsius (C)

The conversion between F and C is computed with the following equations:

   F = C * 9 / 5 + 32

   C = (F - 32) * 5 / 9
   
   For examples,
   ```{r}
   c = 20;    f = c * 9 / 5 + 32
   f
   ```
   ```{r}
   f = 98;    c = (f - 32) * 5 / 9
   c
   ```

--- .class #id

### Distance Conversion between Mile (M) and Kilometer (K)

The conversion between M and K is computed with the following equations:

   K = M * 1.6093

   M = K / 1.6093

For examples,
   ```{r}
   m = 65;    k = m * 1.6093
   k
   ```
   ```{r}
   k = 120;    m = k / 1.6093
   m
   ```

--- .class #id

### Volume Conversion between Gallon (G) and Liter (L)

The conversion between G and L is computed with the following equations:

   L = G * 3.7854

   G = L / 3.7854
   
   For examples,
   ```{r}
   g = 12;    l = g * 3.7854
   l
   ```
   ```{r}
   l = 50;    g = l / 3.7854
   g
   ```

